Analysis of Security-Cost Trade-off of Fully Homomorphic Encryption Schemes

### 2013-06-12 Report/article.tex
test.c in Evlauation phase
modif

@@

@@

@@

 \caption{Min-Max\label{Code:algo}}

@@

\item KeyGen\\
The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ shows a variation from 0.31 s to 13.41 s with mean = 2.726 s.\\
\item {Encryption and Decryption}\\

\item {Cost time of Min-Max program}\\
\begin{tabular}{|c|c|c|c|c|c|c|c|c|c|}
  \hline
  nbits  & 3 & 4 & 5 & 6 & 7 & 8 &  9  & 10 \\
  \hline
  time(s) & 4.17 & 5.84 & 7.18 & 4.29 & 4.65 & 5.9 & 6.71 & 6.73\\
  \hline
\end{tabular}
\end{itemize}
\section{Choice of Benchmarks}

>>>>

 \KwData{a':=$(a_0',a_1',\ldots, a_{n-1}'$), b':=$(b_0',b_1',\ldots, b_{n-1}')$ }

 \KwResult{Return Max(a',b') and Min(a',b')}

@@

     $aIsGreater \leftarrow (aIsGreater +\neg(b_i')a_i')* bitEqual$ \;
     $bitEqual \leftarrow bitEqual*(a_i'b_i' + \neg(a_i)'*\neg(b_i'))$		       	
 }

@@

     $Max_i \leftarrow aIsGreater*a_i' + \neg(aIsGreater)*b_i'$ \;

     $Min_i \leftarrow  \neg(aIsGreater)*a_i' + aIsGreater*b_i'$ \;

@@

 \caption{Min-Max on ciphertext \label{Code:algo}}

@@

\item KeyGen\\
The measured time execution for KeyGen($N, \mu$)  for fixed values of parameters: $N=8$ and $\mu = 4$ show a variation from 0.2 s to 14.41 s with big density at the interval [0.2s, 1s].\\
\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=5cm]{f3.eps} 
\caption{Run time of KeyGen(ms)} 
\label{image_f2} %l'étiquette pour faire référence à cette image
\end{figure}
\item {Encryption and Decryption}\\

\item {Cost time of Min-Max program}\\
We measure the run time from $n=1$ to $32$ bits,we find a linear cost which confirms the $\theta(n)$ complexity. During these measures the result of Min-Max is correct. 
\begin{figure}[!h] %on ouvre l'environnement figure
\centering
\includegraphics[width=5cm]{f2.eps} 
\caption{Run time(ms)} 
\label{image_f2} %l'étiquette pour faire référence à cette image
\end{figure}

\item The cost of this algorithm on ciphertext is linear with bit number, like  the algorithm on plaintext, the extra cost in this case is encryption-decryption cost and especially the code generation which is very inpreductible and take often a long time in the SV-Scheme.
\end{itemize}
\section{Choice of Benchmarks}
